Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Pointed the tex to the clean bibliography
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1613 0ae5e6b2-d358-4f09-a895-f82f13dd62a4
add variational hook
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1614 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\title{Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings and Other Goodies }

@@

%% use of expectation and variance semiring
The first- and second-order expectation semirings can be used compute many interesting quantities over the hypergraph.
These quantities include expected hypothesis length, feature expectation, entropy, cross-entropy, Kullback-Leibler divergence,
Bayes risk, variance of hypothesis length, gradient of entropy and Bayes risk, covariance and Hessian matrix, and so on.
% The second-order expectation semiring is essential for many interesting training paradigms 
% such as deterministic annealing \cite{Rose98deterministicannealing}, minimum risk \cite{smith-eisner:2006:POS},
% active and semi-supervised learning \cite{entropy-mini,semiCRF-jiao}.
% In these settings, we must compute the gradient of entropy or risk. 
% The semiring can also be used for second-order gradient optimization algorithms.

\section{Hypergraph-based Discriminative Training}
\todo{zhifei}

\cite{variational-decoding-acl09}
\cite{oracle-extraction-naacl09}

@@

\bibliographystyle{acl}
\bibliography{machinetranslation-clean}

>>>>

\title{Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies }

@@

%% use of expectation and variance semiring
The first- and second-order expectation semirings can be used compute many interesting quantities over the hypergraph.
These quantities include expected hypothesis length, feature expectation, entropy, cross-entropy, Kullback-Leibler divergence,
Bayes risk, variance of hypothesis length, gradient of entropy and Bayes risk, covariance and Hessian matrix, and so on.

% The second-order expectation semiring is essential for many interesting training paradigms 
% such as deterministic annealing \cite{Rose98deterministicannealing}, minimum risk \cite{smith-eisner:2006:POS},
% active and semi-supervised learning \cite{entropy-mini,semiCRF-jiao}.
% In these settings, we must compute the gradient of entropy or risk. 
% The semiring can also be used for second-order gradient optimization algorithms.

\section{Variational Decoding}
Statistical models in machine translation exhibit spurious ambiguity.
That is, the probability of an output string is split
among many distinct derivations (e.g., trees or
segmentations). In principle, the goodness of a
string is measured by the total probability of its
many derivations. However, finding the best string
(e.g., during decoding) is then computationally intractable.
Therefore, the first version implemented the Viterbi ?????Joshua most systems use a simple
Viterbi approximation that measures the goodness 
of a string using only its most probable derivation.

Instead, we develop a variational approximation \cite{variational-decoding-acl09},
which considers all the derivations but still
allows tractable decoding.

\section{Hypergraph-based Discriminative Training}
Discriminative training with a large number of features has 
great potential to improve the MT performance.
We have implemented the hypergraph-based

\cite{oracle-extraction-naacl09}

@@

\bibliographystyle{acl}
\bibliography{machinetranslation}
